Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Paper: Legacy figures removed, caption, minor improvements.

\author{
  Patrick Bänziger, Kaspar Etter, Jan Rüegg\\
  Department of Computer Science, ETH Zurich, Switzerland
}

@@

\begin{tikzpicture}[node distance = 2cm, auto]
  % Place nodes
  \node [cloud] (node1) {Start};
  \node [block, right of=node1, node distance = 3.1cm] (node2) {Remove validation set};
  \node [block, below of=node2] (node3) {Frame image};
  \node [block, below of=node3] (node4) {Gaussian interpolation};
  \node [decision, below of=node4] (node5) {Iterative?};
  \node [block, right of=node5, node distance = 3.1cm, fill=green!20] (node6) {Find best threshold};
  \node [block, below of=node6, fill=green!20] (node7) {Reset known values except validation set};

@@

  \path [line] (node7) |- (node11);
\end{tikzpicture}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/imageFraming.png}
  \caption{Only the inner patch (marked red) is reconstructed in one step while the frame only provides additional signal. (Undistorted image shown) }
  \label{fig:framing}
\end{figure}

@@

\begin{figure*}[b]
  \centering
  \includegraphics[width= 400px]{images/flowchart}
  \caption{The algorithm as a flow chart}
  \label{fig:flowchart}
\end{figure*}
\end{document}

>>>>

\author{
  Group: NoobzRockz\\
  Patrick Bänziger, Kaspar Etter, Jan Rüegg\\
  Department of Computer Science, ETH Zurich, Switzerland
}

@@

\begin{figure}
\begin{tikzpicture}[node distance = 2cm, auto]
  % Place nodes
  \node [cloud] (node1) {Start};
  \node [block, right of=node1, node distance = 3.1cm] (node2) {Remove validation set};
  \node [block, below of=node2] (node3) {Frame image};
  \node [block, below of=node3] (node4) {Gaussian interpolation};
  \node [decision, below of=node4] (node5) {Iterative?};
  \node [block, right of=node5, node distance = 3.1cm, fill=green!20] (node6) {Find best threshold};
  \node [block, below of=node6, fill=green!20] (node7) {Reset known values except validation set};

@@

  \path [line] (node7) |- (node11);
\end{tikzpicture}
\caption{Our newly proposed algorithm as a flowchart.}
\end{figure}

@@

@@

\end{document}
